Tables and Figures - Supplement A and B

### 2019-12-04 code/05_figures-and-correlations.rmd
Correction to Figure 3 and added Supplement C

```{r corr_per_effect_type-prep}
#Each set of input datapoints is meta-analyzed as per the original replication project
#Then correlated with tau2 per effect type
#Function 'est_heterogen_smd_raw' is sourced, see also tables.rmd
tau2_per_type <- dat %>% 
  split(.$effect) %>%  
  map_dfr(est_heterogen_smd_raw, .id = "effect")

MD_fit <- function(x){
    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, data = x)
    hetero <- confint(fit)$random[c(1, 3), ] 
    data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3],
             H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
}

log_or_fit <- function(x){ #NB! if a cell is 0, 1/2 will be added to it
    fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
    hetero <- confint(fit)$random[c(1, 3), ] 
    data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3],
             H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
}

#Raw mean differences to SMD
MD_standardized <- dat %>% 
  filter(outcomes1_2 == "mean _ SD") %>% #Note, drops Mean _ SE study since no method in metafor to convert into standardized mean differences
  split(.$effect) %>% 
  map_dfr(MD_fit, .id = "effect")

@@

log_odds_ratios <- dat %>% 
  filter(effect %in% c(OR2d, ml2_or, rd_effects)) %>% 
  split(.$effect) %>% 
  map_dfr(log_or_fit, .id = "effect")

#One with NA values: ML2; Trolley dilemma 1; Site = 'cas'

tau2_per_type <- dat %>% #This is to add the effect_type names
  select(effect, effect_type) %>% 
  distinct() %>% #get unique rows
  mutate(effect_type = recode(effect_type, 
                              d = "Standardized Mean Difference")) %>% 
  left_join(tau2_per_type) %>% #Add the meta-analytic results
  filter(!effect %in% c(log_odds_ratios$effect, MD_standardized$effect)) %>% #drop old odds ratio effects and unstandardized MD
  bind_rows(MD_standardized) %>% #add MD after standardization
  bind_rows(log_odds_ratios) %>% #add odds ratios
  mutate(effect_type = ifelse(effect %in% MD_standardized$effect, "Standardized Mean Difference", effect_type),
         effect_type = ifelse(effect %in% log_odds_ratios$effect, "Log Odds Ratio", effect_type),
         eff_size = abs(eff_size)) %>% #need the absolute values for plotting
  filter(effect_type %in% c("Standardized Mean Difference", "Log Odds Ratio"))

#labels for figure 3----
fitter <- function(df){  #function to fit correlations for annotating facet plots
 fit_tau2 <- summary(lm(tau2 ~ eff_size, data = df))
 fit_I2 <- summary(lm(s_I2 ~ eff_size, data = df))
 fit_H2 <- summary(lm(H2 ~ eff_size, data = df))
 r <- c(sqrt(fit_tau2$r.squared), sqrt(fit_I2$r.squared), sqrt(fit_H2$r.squared))
 data.frame(r = format(round(r, digits = 2), nsmall = 2),
            index = c("tau2", "I2", "H2")) 
}

#functions to estimate bootstrapped confidence intervals to add to plot correlations
pear_tau2 <- function(formula, data, indices){ #pearson
     d <- data[indices,]
     fit <- cor.test(formula = ~ tau2 + eff_size, data=d)
     return(fit$estimate)
}
pear_I2 <- function(formula, data, indices){ #pearson
     d <- data[indices,]
     fit <- cor.test(formula = ~ s_I2 + eff_size, data=d)
     return(fit$estimate)
}
pear_H2 <- function(formula, data, indices){ #pearson
     d <- data[indices,]
     fit <- cor.test(formula = ~ H2 + eff_size, data=d)
     return(fit$estimate)
}

bootfitter <- function(x){ #function that computes the bootstrapped confidence intervals using above functions to annotate plots
  bootfit <- boot(data=x, statistic=pear_tau2, R=1000, formula= ~ eff_size + tau2)
  tau2_ci_pears <- boot.ci(bootfit, type="perc")
  bootfit <- boot(data=x, statistic=pear_I2, R=1000, formula= ~ eff_size + s_I2)
  I2_ci_pears <- boot.ci(bootfit, type="perc")
  bootfit <- boot(data=x, statistic=pear_H2, R=1000, formula= ~ eff_size + H2)
  H2_ci_pears <- boot.ci(bootfit, type="perc")

  ci.lb <- c(tau2_ci_pears$percent[4], I2_ci_pears$percent[4], H2_ci_pears$percent[4])
  ci.ub <- c(tau2_ci_pears$percent[5], I2_ci_pears$percent[5], H2_ci_pears$percent[5])

  ci <- paste0("[", format(round(ci.lb, 2), nsmall = 2), ", ",
       format(round(ci.ub, 2), nsmall = 2), "]")#percentile 
  data.frame(ci, index = c("tau2", "I2", "H2"))
}

set.seed(435) #for the bootstrapping
fig3_ci <- tau2_per_type %>% 
  split(.$effect_type) %>% 
  map_dfr(bootfitter, .id = "effect_type")

labels <- tau2_per_type %>% #row 1:2 = tau2, row 3:4 = I2, row 5:6 = H2
  split(.$effect_type) %>% 
  map_dfr(fitter, .id = "effect_type") %>%
  mutate(lab = paste0("r = ", r, " ", fig3_ci$ci)) #put output into one variable for improved plotting

@@

```{r corr_per_effect_type-plot, cache = FALSE}
#tau plot----
tau_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = sqrt(tau2))) + #NB! Taking sqrt of tau2 here
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "tau2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste("Between Studies Standard Deviation ", italic(tau)))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#I2plot----
I2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = s_I2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "I2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(I)^2, " Index"))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  coord_cartesian(ylim = c(0, 100)) +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#H2plot----
H2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "H2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(H)^2, " Index"))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

@@

#This section gives the correlations reported in the section 'Heterogeneity and effect sizes' in the main manuscript

#1. Standardized mean differences----
SMDs <- tau2_per_type %>% filter(effect_type == "Standardized Mean Difference") %>% 
  mutate(tau = sqrt(tau2))

@@

@@

#bootstrap confidence intervals
#code by Amir Abdol

#1.1 I2 confidence intervals----
pear <- function(formula, data, indices){ #pearson
     d <- data[indices,]
     fit <- cor.test(formula = ~ s_I2 + eff_size, data=d)
     return(fit$estimate)
}

#bootfit <- boot(data=SMDs, statistic=pear, R=1000, formula= ~ eff_size + s_I2) #see Fig 3
#I2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

#Excluding anchoring effects
set.seed(234)
bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ eff_size + s_I2)

@@

#1.2 Tau2 confidence intervals----
pear <- function(formula, data, indices){
     d <- data[indices,]
     fit <- cor.test(formula = ~ tau + eff_size, data=d)
     return(fit$estimate)
}

# bootfit <- boot(data=tau2_per_type, statistic=pear, R=1000, formula= ~ eff_size + tau2) #see Fig 3
# tau2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))

@@

set.seed(423)
bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ eff_size + tau)
tau_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

#1.3 H2 confidence intervals----
pear <- function(formula, data, indices){
     d <- data[indices,]
     fit <- cor.test(formula = ~ H2 + eff_size, data=d)
     return(fit$estimate)
}

set.seed(342)
bootfit <- boot(data=tau2_per_type, statistic=pear, R=1000, formula= ~ eff_size + H2)
H2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))

#1.4 spearman bootstrap CIs----
#First for I2
spear <- function(formula, data, indices){ #spearman
     d <- data[indices,]
     fit <- cor.test(formula = ~ s_I2 + eff_size, data=d, method = "spearman")
     return(fit$estimate)
}

set.seed(241)
options(warn=-1)
bootfit <- boot(data=tau2_per_type, statistic=spear, R=1000, formula= ~ eff_size + s_I2)
options(warn=0)

@@

#Second for tau
spear <- function(formula, data, indices){ #spearman
     d <- data[indices,]
     fit <- cor.test(formula = ~ tau + eff_size, data=d, method = "spearman")
     return(fit$estimate)
}

set.seed(5233)
tau2_per_type <- tau2_per_type %>% mutate(tau = sqrt(tau2))
options(warn=-1)
bootfit <- boot(data=tau2_per_type, statistic=spear, R=1000, formula= ~ eff_size + tau)
options(warn=0)

>>>>

```{r corr_per_effect_type-prep}

#Function 'est_heterogen_smd_raw' is sourced, see also tables.rmd
tau2_per_type <- dat %>% #First compute meta-analytic results for all effects (will save: SMDs results)
  split(.$effect) %>%  
  map_dfr(est_heterogen_smd_raw, .id = "effect")

#Raw mean differences to SMD
MD_standardized <- dat %>% 
  filter(outcomes1_2 == "mean _ SD") %>% #Note, drops Mean _ SE studies (two) since no method in metafor to convert into standardized mean differences
  split(.$effect) %>% 
  map_dfr(MD_fit, .id = "effect") #MD_fit function is sourced

@@

log_odds_ratios <- dat %>% 
  filter(effect %in% c(OR2d, ml2_or, rd_effects)) %>% 
  split(.$effect) %>% 
  map_dfr(log_or_fit, .id = "effect") #log_or_fit function is sourced

tau_per_type <- dat %>% #This is to add the effect_type names
  select(effect, effect_type) %>% 
  distinct() %>% #get unique rows
  mutate(effect_type = recode(effect_type, 
                              d = "Standardized Mean Difference")) %>% 
  left_join(tau2_per_type) %>% #Add the meta-analytic results
  filter(!effect %in% c(log_odds_ratios$effect, MD_standardized$effect)) %>% #drop old odds ratio effects and unstandardized MD
  bind_rows(MD_standardized) %>% #add MD after standardization
  bind_rows(log_odds_ratios) %>% #add odds ratios
  mutate(effect_type = ifelse(effect %in% MD_standardized$effect, "Standardized Mean Difference", effect_type),
         effect_type = ifelse(effect %in% log_odds_ratios$effect, "Log Odds Ratio", effect_type),
         eff_size = abs(eff_size), #need the absolute values for plotting
         tau = sqrt(tau2)) %>% 
  filter(effect_type %in% c("Standardized Mean Difference", "Log Odds Ratio"))

#lables
set.seed(435) #for the bootstrapping
fig3_ci <- tau_per_type %>% 
  split(.$effect_type) %>% 
  map_dfr(bootfitter, .id = "effect_type") #bootfitter is a sourced function

labels <- tau_per_type %>% #row 1:2 = tau2, row 3:4 = I2, row 5:6 = H2
  split(.$effect_type) %>% 
  map_dfr(fitter, .id = "effect_type") %>% #fitter is a sourced function
  mutate(lab = paste0("r = ", r, " ", fig3_ci$ci)) #put output into one variable for improved plotting

@@

```{r corr_per_effect_type-plot, cache = FALSE}
#tau plot----
tau_facet <- ggplot(tau_per_type, aes(x = eff_size, y = tau)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "tau",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste("Between Studies Standard Deviation ", italic(tau)))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#I2plot----
I2_facet <- ggplot(tau_per_type, aes(x = eff_size, y = s_I2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "I2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(I)^2, " Index"))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  coord_cartesian(ylim = c(0, 100)) +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#H2plot----
H2_facet <- ggplot(tau_per_type, aes(x = eff_size, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "H2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(H)^2, " Index"))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

@@

#This section gives the correlations and values reported in the section 'Heterogeneity and effect sizes' in the main manuscript

#1. Standardized mean differences----
SMDs <- tau_per_type %>% filter(effect_type == "Standardized Mean Difference")

@@

##When effect size == 0, what is average heterogeneity?
mean(SMDs$tau[SMDs$eff_size < 0.05]) #for tau = 0.016
mean(SMDs$s_I2[SMDs$eff_size < 0.05]) #I2 = 3.05
mean(SMDs$H2[SMDs$eff_size < 0.05]) #H2 = 0.88

@@

#bootstrap confidence intervals
#code contribution by Amir Abdol

#1.1 I2 confidence intervals----

#bootfit <- boot(data=SMDs, statistic=pear_I2, R=1000, formula= ~ eff_size + s_I2) #see Fig 3
#I2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

#Excluding anchoring effects
set.seed(234)
bootfit <- boot(data=dropped_anchoring, statistic=pear_I2, R=1000, formula= ~ eff_size + s_I2) #statistic function is sourced

@@

#1.2 Tau confidence intervals----

# bootfit <- boot(data=tau_per_type, statistic=pear_tau, R=1000, formula= ~ eff_size + tau2) #see Fig 3
# tau2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))

@@

set.seed(423)
bootfit <- boot(data=dropped_anchoring, statistic=pear_tau, R=1000, formula= ~ eff_size + tau)
tau_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

#1.3 H2 confidence intervals----
set.seed(342)
bootfit <- boot(data=tau_per_type, statistic=pear_H2, R=1000, formula= ~ eff_size + H2)
H2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))

#1.4 spearman bootstrap CIs----
#First for I2
spear_I2 <- function(formula, data, indices){ #spearman
     d <- data[indices,]
     fit <- cor.test(formula = ~ s_I2 + eff_size, data=d, method = "spearman")
     return(fit$estimate)
}

set.seed(241)
options(warn=-1)
bootfit <- boot(data=tau_per_type, statistic=spear_I2, R=1000, formula= ~ eff_size + s_I2)
options(warn=0)

@@

#Second for tau

set.seed(5233)
options(warn=-1)
bootfit <- boot(data=tau_per_type, statistic=spear_tau, R=1000, formula= ~ eff_size + tau)
options(warn=0)

### 2019-12-04 code/06_Supplement-tables-figures.Rmd
Correction to Figure 3 and added Supplement C

```{r load packages, data and source functions}
if(!require(readr)){install.packages("readr")}
if(!require(metafor)){install.packages("metafor")}
if(!require(dplyr)){install.packages("dplyr")}
if(!require(purrr)){install.packages("purrr")}
if(!require(kableExtra)){install.packages("kablExxtra")}

library(readr) #To load data
library(dplyr) #For data transformation
library(purrr) #For data iteration
library(metafor) #To run meta-analyses
library(ggplot2) #plotting figures
library(cowplot) #combine plots
library(kableExtra) #create fancy pdf tables

@@

>>>>

```{r load packages, data and source functions}
if(!require(readr)){install.packages("readr")}
if(!require(metafor)){install.packages("metafor")}
if(!require(dplyr)){install.packages("dplyr")}
if(!require(purrr)){install.packages("purrr")}
if(!require(kableExtra)){install.packages("kablExxtra")}
if(!require(ggplot2)){install.packages("ggplot2")}
if(!require(cowplot)){install.packages("cowplot")}
if(!require(boot)){install.packages("boot")}

library(readr) #To load data
library(dplyr) #For data transformation
library(purrr) #For data iteration
library(metafor) #To run meta-analyses
library(ggplot2) #plotting figures
library(cowplot) #combine plots
library(kableExtra) #create fancy pdf tables
library(boot) #Bootstrap confidence intervals for correlations

@@

## Supplement C

```{r, preprocessing}

SMDs_raw <- dat %>% filter(outcomes1_2 == "mean _ SD") %>% 
  mutate(wi = compute_precision(SD1 = outcome_t2, SD2 = outcome_c2, n1 = ntreatment, n2 = ncontrol)) #compute_precision function is sourced

average_within <- SMDs_raw %>% #these values we now wish to correlate with meta-analytic results
  group_by(effect) %>% 
  summarize(s2 = sum(wi) * (n()-1) / (sum(wi)^2 - sum(wi^2))) %>% #Average within study variance; equation 9. Higgins and Thompson (2003). n() = k [number of studies in a meta-analysis]
  ungroup()

#Raw mean differences to SMD
MD_standardized <- dat %>% 
  filter(outcomes1_2 == "mean _ SD") %>% #Note, drops Mean _ SE studies (two) since no method in metafor to convert into standardized mean differences
  split(.$effect) %>% 
  map_dfr(MD_fit, .id = "effect") #MD_fit function is sourced

tau_per_type <- MD_standardized %>% 
  left_join(average_within) %>%
  mutate(sigma = sqrt(s2),
         eff_size = abs(eff_size),
         tau = sqrt(tau2)) #needed for bootfitter function below to work but not used

#Add labels
#lables
set.seed(499) #for the bootstrapping
all_effects_ci <- tau_per_type %>% 
  bootfitter_sigma(.) #bootfitter is a sourced function

labels_all <- tau_per_type %>% #
  fitter_sigma(.) %>% #fitter is a sourced function
  mutate(lab = paste0("r = ", r, " ", all_effects_ci$ci)) #put output into one variable for improved plotting

#As above but dropping the 4 largest effect sizes (Anchoring effects)----
without_anchoring <- tau_per_type %>% 
  filter(!grepl("Anchoring", effect))

#lables
set.seed(500) #for the bootstrapping
restricted_effects_ci <- without_anchoring %>% 
  bootfitter_sigma(.) #bootfitter is a sourced function

labels_restricted <- without_anchoring %>% #row 1:2 = tau2, row 3:4 = I2, row 5:6 = H2
  fitter_sigma(.) %>% #fitter is a sourced function
  mutate(lab = paste0("r = ", r, " ", restricted_effects_ci$ci)) #put output into one variable for improved plotting

```{r}

within_plot_full <- ggplot(tau_per_type, aes(x = eff_size, y = sigma)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels_all[labels_all$index == "sigma",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste("Within Studies Standard Deviation"))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid"))

without_anchoring_plot <- ggplot(without_anchoring, aes(x = eff_size, y = sigma)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels_restricted[labels_restricted$index == "sigma",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste("Within Studies Standard Deviation"))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid"))

cowplot::plot_grid(within_plot_full, without_anchoring_plot, nrow = 2, labels = "AUTO")
ggsave("../figures/figure-S2.png", dpi = 600, height =  7, width = 7)
```

Figure S2. The Pearson correlation (_r_) between average absolute effect size and average within studies standard deviation for 40 effects that were measured as mean or standardized mean differences. Panel A shows results for all 40 effect sizes and panel B with the four largest (Anchoring 1 - 4) excluded. Effects reported as mean differences were standardized. Square brackets contain 95% bootstrapped percentile confidence intervals.
